### 2011-05-12 paper.tex

Each oracle call queries some input to check if it is $g$. There is a function $h \in C$ and a polynomial $r$ such that $g(x) = 1$ if and only if $h(\langle x,y\rangle) = 1$ for an odd number of $y\in\{0,1\}^{r(|x|)}$, and $g(x) = 0$ otherwise. Thus, $f \in \parity \cdot C$.

To show that $f$ is in $\parity \cdot C$, we guess the following bits for a given input $x$:
\begin{itemize}
\item Bits $a_1,a_2,...,a_{p(|x|)}$. Intuitively, these will be the answers to the oracle calls made by $T$.
\item Bits $b_1,b_2,...,b_{p(|x|)}$. The purpose of these will become clear later.
\item Strings $y_1,y_2,...,y_{p(|x|)}$, each of length $r(q(|x|))$. These are the strings that an oracle call guesses.
\end{itemize}
After guessing, we do the following polynomial time reduction to $\intersect(h)$. For an input $x$, simulate $T$ using the bits $a_1,a_2,...,a_{p(|x|)}$ as the answers to the oracle calls (taking $1$ to mean that the oracle call accepted, and $0$ to mean that the oracle call rejected). If $T$ would reject, then reject.

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $h(x_i, y_i)$
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $\overline{h}(x_i,y_i) = 1$. We can do this with a call to $\intersect(h)$.

(Technical note: it is possible that some bits out of the $a_i$, $b_i$, and $y_i$ are not used. It is possible that not all $p(x)$ oracle calls will be made, or that not all $r(q(|x|))$ bits of a $y_i$ will be used, if $|x_i| < q(|x|)$. Thus, we also say that $(a_i, b_i, y_i)$ is not good if any unused bits are nonzero.)

Why does this give us what we want? We want to show that this will accept for an odd number of choices of the $a_i$, $b_i$, and $y_i$ if and only if $f(x) = 1$. Let $\# (a_1,...,a_{p(|x|)})$ be the number of ways to choose the $b_i$, and $y_i$ such that all triples $(a_i,b_i,y_i)$ are good. Then the total number of accepting paths is
\begin{center}$\displaystyle \sum_{a_1,...,a_{p(|x|)}\text{ such that $T$ accepts}}  \#(a_1,...,a_{p(|x|)})$\end{center}
We claim that $ \#(a_1,...,a_{p(|x|)})$ is odd if and only if $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls. This follows from the way we chose to decide if $(a_i, b_i, y_i)$ is good. If $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls, then for each $i$, there are an odd number of $(b_i,y_i)$ such that $(a_i, b_i, y_i)$ is good. If $a_i = 1$, all good triples will have $b_i = 1$, so the parity is determined by the number of $y_i$ for which $P$ accepts $(x_i, y_i)$. But if $a_i = 1$, then this should be odd. If $a_i = 0$, then the number of $y_i$ for which $P$ accepts $(x_i, y_i)$ is even. However, we get one more good pair, namely $(0,0,0)$.

>>>>

The $i^\text{th}$ oracle call queries some input $x_i$ to check if $g(x_i) = 1$. There is a function $h \in C$ and a polynomial $r$ such that for any query string $x_i$, we have $g(x_i) = 1$ if and only if $h(\langle x_i,y\rangle) = 1$ for an odd number of $y\in\{0,1\}^{r(|x|)}$, and $g(x_i) = 0$ otherwise. Thus, $f \in \parity \cdot C$.

To show that $f$ is in $\parity \cdot C$, we guess the following bits for a given input $x$:
\begin{itemize}
\item Bits $a_1,a_2,...,a_{p(|x|)}$. Intuitively, these will be the answers to the oracle calls made by $T$.
\item Bits $b_1,b_2,...,b_{p(|x|)}$. The purpose of these will become clear later; they will be necessary for fixing the parity of some numbers.
\item Strings $y_1,y_2,...,y_{p(|x|)}$, each of length $r(q(|x|))$. These are the strings that an oracle call guesses.
\end{itemize}
After guessing, we do the following polynomial time reduction to $\intersect(h)$. For an input $x$, simulate $T$ using the bits $a_1,a_2,...,a_{p(|x|)}$ as the answers to the oracle calls (taking $1$ to mean that the oracle call accepted, and $0$ to mean that the oracle call rejected). If $T$ would reject, then reject.

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $h(x_i, y_i)$
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $h(x_i,y_i) = 1$. We can do this with a call to $\intersect(h)$.

(Technical note: it is possible that some bits out of the $a_i$, $b_i$, and $y_i$ are not used. It is possible that not all $p(x)$ oracle calls will be made, or that not all $r(q(|x|))$ bits of a $y_i$ will be used, if $|x_i| < q(|x|)$. Thus, we require that all unused bits be $0$ for $(a_i, b_i, y_i)$ to be good. In that case that there is no $i^\text{th}$ oracle call, the only good triple $(a_i, b_i, y_i)$ is the all zeroes triple.)

Why does this give us what we want? We want to show that this will accept for an odd number of choices of the $a_i$, $b_i$, and $y_i$ if and only if $f(x) = 1$. Let $\# (a_1,...,a_{p(|x|)})$ be the number of ways to choose the $b_i$, and $y_i$ such that all triples $(a_i,b_i,y_i)$ are good. Then the total number of accepting paths is
\begin{center}$\displaystyle \sum_{a_1,...,a_{p(|x|)}\text{ such that $T$ accepts}}  \#(a_1,...,a_{p(|x|)})$\end{center}
We claim that $ \#(a_1,...,a_{p(|x|)})$ is odd if and only if $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls. This follows from the way we chose to decide if $(a_i, b_i, y_i)$ is good. If $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls, then for each $i$, there are an odd number of $(b_i,y_i)$ such that $(a_i, b_i, y_i)$ is good. If $a_i = 1$, all good triples will have $b_i = 1$, so the parity is determined by the number of $y_i$ for which $h(x_i, y_i)=1$. But since $a_i = 1$, then this should be odd. In the other case, if $a_i = 0$, then the number of $y_i$ for which $h(x_i, y_i)=1$ is even. However, we get one more good pair, namely $(0,0,0)$.
